\documentclass[12pt]{article}
\usepackage{color,soul}
% Import preambles and macros for notes
\input{../../../../preambles/notes-preamble.tex}
\input{../../../../preambles/notes-macros.tex}
\input{../../../../preambles/theorem-system-subsection.tex}

\title{MATH 301 Lecture 8}
\author{Deepak Jassal}
\date{February 4\textsuperscript{th}, 2026}

\begin{document}
\maketitle
\section{Complex Differentiability}
\defn{Complex Derivatives}{
    \begin{enumerate}
        \item Let $A$ be an open subsest of $\C$ and $z_0\in A$ and let $f:A\to\C$. Then $f$ is differentiable at $z_0$ if the limit
            \[
                f'(z_0)=\lim_{f(z)-f(z_0)}{z-z_0} \tag{$\ast$}
            \]
            exists.
        \item $f$ is called analytic at $z_0$ if $f'(z)$ in some nieghbourhood of $f(z_0)$. This means that the limit is the same if $z\to z_0$ by any path.
    \end{enumerate}
}
For the limit $\ast$ to exist is means that. For all $\varepsilon>0$ there exists $\delta>0$ such that 
\[
    0<|z-z_0|<\delta\Rightarrow \left|\frac{f(z)-f(z_0)}{z-z_0}\right|=|f'(z_0)|<\varepsilon.
\]
Writing $\ast$ as $F(z)$ we say the above means
\[
    \lim_{z\to z_0}F(z)=f'(z_0).
\]
\textit{Note:} Analytic and holomorphic are synonymous in this context.
\prop{
    Suppose that $f,g$ are analytic functions on an open set $A\subseteq\C$. Then
    \begin{enumerate}
        \item $af+bg$ is analytic on $A$, $\forall a,b\in\C$.
        \item $(fg)'=f'g+fg'$
        \item $\left(\dfrac{f}{g}\right)'=\dfrac{f'g-g'f}{g^2}$ provided $g\neq0$ on $A$.
        \item The chain rule is also valid:\\
        If $f:A\to\C$ with $A$ open is analytic, and $g:B\to\C$ with $B$ open is analytic and $f(A)\subseteq B$
        \[
            (f(g(z)))'=f'(g(z))g'(z).
        \]
        \item If $\gamma:(a,b)\to\C$ with $(a,b)\subseteq\R$ if differentiable, and $f:A\to\C$ with $A$ open is analytic. Then
        \[
            \frac{d}{dt}f(\gamma(t))=f'(\gamma(t))\gamma'(t).
        \]
        provided that $\gamma((a,b))\subseteq\C$.
    \end{enumerate}
 }
 \subsection{Conformal Mapping Theorem}
\thm{Conformal Mapping Theorem}{
    Let $A\subseteq\C$ be an open set, and $f:A\to\C$ is analytic on $A$. Further suppose that $\gamma:I\to A$, where $I$ is an open interval containing 0, is differentiable, $z_0\in A$, $\gamma(0)=z_0,$ and $\gamma'(0)=v\neq0$. Also suppose that $f'(z_0)\neq0$. Then there exists $0<r\in\R$ and $\theta\in[0,2\pi)$ such that if
    \[
        u=\frac{d}{dt}f(\gamma(t))\vert_0
    \] 
    then 
    \begin{enumerate}
        \item $|u|=r|v|$;
        \item arg$u=$arg$v+\theta$ mod$2\pi$.
    \end{enumerate}
    We say that $f$ is conformal at $z_0$
}
\textit{Note:} also that a conformal map preserves the orientation of tangent vectors. It preserves angles but not always lengths.
\pf[Proof of Theorem 1.1.1]{
    \[
        u=\frac{d}{dt}f(\gamma(t))\vert_0=f'(\gamma(0))\gamma'(0)=f'(z_0)v.
    \]
    \[
        \Rightarrow |u|=|f'(z_0)||v|
    \]
    \[
        \arg(u)=\arg(v)+\arg(f'(z_0))
    \]
    Now define $r=|f'(z_0)|>0$ and $\theta=\arg(f(z_0))$.
}
\subsection{Cauchy-Riemann Equation}
Let $f:A\to\C$, $\mu:\C\to\R^2$ be defined as \[\mu(z)=\mu(x+iy)=(x,y).\] Then $f(x+iy)$ can be written as 
\[
    f(x+iy)=u(x,y)+v(x,y)
\]
where 
\[
    u:\mu(A)\to\R
\]
\[
    v:\mu(A)\to\R.
\]
\ex{
    $f(z)=z^2=(x+iy)^2=x^2-y^2+2xy$ where $u(x,y)=x^2-y^2$ and $v(x,y)=2xy$.
}
\thm{}{
    Let $f:A\to\C,\,z_0\in A$ and $z=x+iy$
    \[
        f(z)=u(x,y)+iv(x,y)
    \]
    \begin{enumerate}
        \item If $f'(z_0)$ exists Then
        $u_x(x_0,y_0)=u_y(x_0,y_0)$ and $v_x(x_0,y_0)=-v_y(x_0,y_0)$.\\
        These are called the Cauchy-Riemann equations.
        \item If $u_x,u_y,v_x,v_y$ are continuous on $\mu(A)$ and satisfy the Cauchy-Riemann equations then $f$ is analytic on $A$. 
    \end{enumerate}
}
\pf[Proof of Theorem 1.2.1]{
    \begin{enumerate}
        \item 
        \[
            \lim_{z\to z_0}\frac{f(z)-f(z_0)}{z-z_0}
        \]
        exists. We calculate it along two paths
        \begin{enumerate}[label=(\roman*)]
            \item $L:x+iy_0\to x_0+iy_0$ where $y_0$ is a constant.
            \[
                \lim_{z\to z_0}f'(z_0)=\lim_{x\to x_0}f^\ast(z)=u_x(x_0,y_0)+iv_x(x_0,y_0).
            \]
            \item $L:x_0+iy\to x_0+iy_0$
            \[
                \lim_{z\to z_0}f'(z_0)=\lim_{y\to y_0}f^\ast(z)=u_y(x_0,y_0)+iv_y(x_0,y_0).
            \]
        \end{enumerate}
        Since $f'(z_0)$ exists we must have that $u_y(x_0,y_0)+iv_y(x_0,y_0)=u_x(x_0,y_0)+iv_x(x_0,y_0)$.
    \end{enumerate}
}

\end{document}