\documentclass[12pt]{article}

% Import preambles and macros for homework
\input{../../../preambles/hw-preamble.tex}
\input{../../../preambles/homework-macros.tex}
\input{../../../preambles/homework-title.tex}
\input{../../../preambles/homework-config.tex}

\renewcommand{\author}{Deepak Jassal}
\renewcommand{\authorlast}{Jassal}
\renewcommand{\coursename}{Number Theory}
\renewcommand{\coursecode}{MATH 480}
\renewcommand{\assignment}{Assignment 4}
\renewcommand{\instructor}{Dr. Alia Hamieh}
\renewcommand{\duedate}{November 20\textsuperscript{th}, 2025}


\begin{document}
\begin{titlepage}
	\centering
	\vspace*{2.0cm}	
	\pgfornament{84}\\
	{\LARGE \textsc{\coursename}\par}
	\vspace{0.5cm}
	{\large\coursecode\par}
    \vspace{0.5cm}
    {\large\instructor\par}
	\vspace{1.5cm}
	{\huge\bfseries\assignment\par}
	\vspace{1cm}  
	{\LARGE\itshape\author\par}
    \vspace{2cm}
	{\large\bfseries Due Date:\par}
	\vspace{0.5cm}
	{\Large \duedate}\\
	\pgfornament{84}
\end{titlepage}
\stepcounter{section}
\section*{Question 1 [2 marks]}
Find all the primitive roots modulo 27.\\
$27=3^3$. $\varphi(3)=2$, by \textit{lemma 2.8.13} the number of integers less than 3 of order 2 do not exceed $\varphi(2)=1$. Also, by \textit{theorem 2.8.9} we know that 3 has a primitive root. Since $2^1\not\equiv 1 \mod 3$ and $2^2\equiv 1 \mod 3$ we have 2 as a primitive root of 3. By \textit{theorem 2.8.15} we know that either $2$ or $2+3=5$ is a primitive root(s) for 9. $\varphi(9)=6$, so we need to check to see if the order of 2 or 5 are 6 in modulo 9. 
\[
	2^1=2,\,2^2=4,\,2^3=8,\,2^4=16\equiv 7,\,2^5=32\equiv 5\mod 9,\,2^6\equiv 5\times2\equiv1\mod 9,
\]
and 
\begin{align*}
	5^1=5,\,5^2=25\equiv 7,\,5^3\equiv 7\times5=&35\equiv8\mod 9,\,5^4\equiv8\times5\equiv 4,\\5^5\equiv4\times5\equiv 2\mod 9,&\,5^6\equiv 2\times5\equiv1\mod 9.	
\end{align*}
So, both 2 and 5 are primitive roots of 9. From \textit{theorem 2.8.16} we know that both 2 and 5 are primitive roots of 27. The other primitive roots of 27 are of the form $2^a$ where $a$ is any integer mod 27 such that $\gcd(a,\phi(27))=\gcd(a,18)=1$. These integers are 1,5,7,11,13,17.
\[
	\begin{aligned}
		2^1 &\equiv 2 \\
		2^5 &\equiv 32 \equiv 5 \\
		2^7 &\equiv 2^5 \cdot 2^2 \equiv 5 \cdot 4 = 20 \\
		2^{11} &= 2^9 \cdot 2^2 \equiv (-1) \cdot 4 \equiv 23 \\
		2^{13} &= 2^9 \cdot 2^4 \equiv (-1) \cdot 16 \equiv 11 \\
		2^{17} &= 2^9 \cdot 2^8 \equiv (-1) \cdot 13 \equiv 14
	\end{aligned}
\]
So the primitive roots of 27 are 2,5,20,23,11,14.


\stepcounter{section}
\section*{Question 2 [2 marks]}
Evaluate $\displaystyle{ \left(\frac{105}{1009}\right)}$.\\
\[
	\left(\frac{105}{1009}\right)=\left(\frac{3}{1009}\right)\left(\frac{5}{1009}\right)\left(\frac{7}{1009}\right)
\] 
By \textit{theorem 3.2.1} we have
\[
	\left(\frac{105}{1009}\right)=\left(\frac{1009}{3}\right)\left(\frac{1009}{5}\right)\left(\frac{1009}{7}\right)
\] 
\[
	\left(\frac{105}{1009}\right)=\left(\frac{1}{3}\right)\left(\frac{4}{5}\right)\left(\frac{1}{7}\right)
\] 
\[
	\left(\frac{105}{1009}\right)=\left(\frac{1}{3}\right)\left(\frac{2}{5}\right)\left(\frac{2}{5}\right)\left(\frac{1}{7}\right)
\] 
\[
	\left(\frac{105}{1009}\right)=\left(\frac{-1}{3}\right)\left(\frac{-1}{3}\right)\left(-1\right)\left(-1\right)\left(\frac{-1}{7}\right)\left(\frac{-1}{7}\right)
\]
\[
	\left(\frac{105}{1009}\right)=\left(-1\right)\left(-1\right)\left(-1\right)\left(-1\right)\left(-1\right)\left(-1\right)=1
\] 


\stepcounter{section}
\section*{Question 3 [3 marks]}
Let $m$ be a positive integer with a primitive root. Suppose that $(a,m)=1$. Prove that then the congruence $x^n\equiv a\mod m$ has exactly $(n,\phi(m))$  solutions if and only if $a^{\frac{\phi(m)}{(\phi(m),n)}}\equiv 1\mod m$.

\stepcounter{section}
\section*{Question 4 [3 marks]}
Let $p$ be an odd prime number, and suppose that $h \geq 2$. Denote by $g$ a primitive root modulo $p^{h}$.
\begin{enumerate}[label=(\alph*)]
    \item List all the solutions of the congruence $x^{p} \equiv 1 \pmod{p^{h}}$  using the primitive root $g$ modulo $p^{h}$.
    \item  List all the solutions of the congruence $x^{2p} \equiv 1 \pmod{p^{h}}$ using the primitive root $g$ modulo $p^{h}$.
\end{enumerate}

\stepcounter{section}
\section*{Question 5 [2 marks]}
Let $n$ be a positive integer with a primitive root. Using this primitive root, prove that the product of all positive integers less than $n$ and relatively prime to $n$ is congruent to $-1$ modulo $n$.

\stepcounter{section}
\section*{Question 6 [2 marks]}
Let $p_{1},p_{2},\ldots,p_{r}$ be distinct prime numbers. Show that there exists an integer $g$ such  that $g$ is a primitive root modulo $p_{i}$ for all $1 \leq i \leq r$.

\stepcounter{section}
\section*{Question 7 [2 marks]}
\begin{enumerate}[label=(\alph*)]
    \item Let $a$ be an integer with $a \geq 2$, and suppose that $q \in \mathbb{N}$. What is the smallest positive integer $d$ satisfying the property that $a^{d} \equiv 1 \pmod{a^{q}-1}$? Deduce that $q$ divides
    $\varphi(a^{q}-1)$.
    \item Let $q$ be a prime number. By considering the prime factorisation of the integer $N = a^{q}-1$, show that either $N$ is divisible by $q$, or else $N$ is divisible by a prime number $p$ with $p \equiv 1 \pmod{q}$.
\end{enumerate}

\stepcounter{section}
\section*{Question 8 [3 marks]}
Let $q$ be a prime number. Prove that there are infinitely many prime
numbers $p$ with $p \equiv 1 \pmod{q}$.

\stepcounter{section}
\section*{Question 9 [3 marks]}
Let $p\geq 5$ be an odd prime, show that
\[ 
    \left(\frac{3}{p}\right)=\begin{cases} 1\:\:\: \text{if}\:\:\: p\equiv \pm1\mod{12}\\ -1\:\:\: \text{if}\:\:\: p\equiv \pm5\mod{12}.\end{cases}
\] 

\stepcounter{section}
\section*{Question 10 [6 marks]}
Let $n>1$ be an odd integer. Write $n=p_1^{e_1}\cdots p_k^{e_k}$. Let $a$ be an integer. We define the {\bf Jacobi symbol} $\left(\frac{a}{n}\right)$ as follows:
\[\left(\frac{a}{n}\right)=\left(\frac{a}{p_1}\right)^{e_1}\cdots \left(\frac{a}{p_k}\right)^{e_k}.\]
Prove the following properties:
\begin{enumerate}[label=(\alph*)]
    \item If $a\equiv b\mod n$, then $\left(\frac{a}{n}\right)=\left(\frac{b}{n}\right)$.
    \item If $a$ and $b$ are integers, then $\left(\frac{a}{n}\right)\left(\frac{b}{n}\right)=\left(\frac{ab}{n}\right)$.
    \item If $x^2\equiv a\mod n$ has a solution, then $\left(\frac{a}{n}\right)=1$. Provide an example that shows that the converse of this statement isn't always true. 
    \item If $m,n$ are relatively prime odd integers, then \[\left(\frac{m}{n}\right)\left(\frac{n}{m}\right)=(-1)^{\frac{m-1}{2}}(-1)^{\frac{n-1}{2}}.\]
\end{enumerate}
\end{document}