\documentclass[12pt]{article}

% Import preambles and macros for homework
\input{../../../../preambles/hw-preamble.tex}
\input{../../../../preambles/homework-macros.tex}
\input{../../../../preambles/homework-title.tex}
\input{../../../../preambles/homework-config.tex}

\renewcommand{\author}{Deepak Jassal}
\renewcommand{\authorlast}{Jassal}
\renewcommand{\coursename}{Introductory Complex Analysis}
\renewcommand{\coursecode}{MATH 301}
\renewcommand{\assignment}{Assignment 2}
\renewcommand{\instructor}{Dr. Edward Dobrowolski}
\renewcommand{\duedate}{January 30\textsuperscript{th}, 2026}


\begin{document}
\begin{titlepage}
	\centering
	\vspace*{2.0cm}	
	\pgfornament{84}\\
	{\LARGE \textsc{\coursename}\par}
	\vspace{0.5cm}
	{\large\coursecode\par}
    \vspace{0.5cm}
    {\large\instructor\par}
	\vspace{1.5cm}
	{\huge\bfseries\assignment\par}
	\vspace{1cm}  
	{\LARGE\itshape\author\par}
    \vspace{2cm}
	{\large\bfseries Due Date:\par}
	\vspace{0.5cm}
	{\Large \duedate}\\
	\pgfornament{84}
\end{titlepage}
\stepcounter{section}
\section*{Problem 1}
Show that is $w\in\C$ then 
\begin{enumerate}[label=(\alph*)]
    \item $|\Re w|\leq |w|$
    \begin{proof}
        Let $w=a+bi$ with $a,b\in\R$. Then we have
        \begin{align*}
            a^2&\leq a^2+b^2\\
            \sqrt{a^2}&\leq \sqrt{a^2+b^2}\\
            |\Re w|&\leq |w|.\qedhere
        \end{align*}
    \end{proof}
    \item $|\Im w|\leq |w|$
    \begin{proof}
        Let $w=a+bi$ with $a,b\in\R$. Then we have
        \begin{align*}
            b^2&\leq a^2+b^2\\
            \sqrt{b^2}&\leq \sqrt{a^2+b^2}\\
            |\Im w|&\leq |w|.\qedhere
        \end{align*}
    \end{proof}
    \item $|w|\leq |\Re w|+|\Im w|$
    \begin{proof}
        Let $w=a+bi$ with $a,b\in\R$. Then we have
        \begin{align*}
            x+y&\leq x+2\sqrt{xy}+y\\
            x+y&\leq(\sqrt{x}+\sqrt{y})^2\\
            \sqrt{x+y}&\leq\sqrt{x}+\sqrt{y},
        \end{align*}
        set $x=a^2$ and $y=b^2$ and we get
        \begin{align*}
            \sqrt{a^2+b^2}&\leq\sqrt{a^2}+\sqrt{b^2}\\
            |w|&\leq|\Re w|+|\Im w|.\qedhere
        \end{align*}
    \end{proof}
\end{enumerate}
\newpage
\stepcounter{section}
\section*{Problem 2a}
Show that 
\[
    |\Re z_1-\Re z_2|\leq |z_1-z_2|\leq |\Re z_1-\Re z_2|+|\Im z_1-\Im z_2|
\]
\begin{proof}
    Let $z_1=a_1+b_1i$, $z_2=a_2+b_2i$ and $z=z_1-z_2=(a_1-a_2)+(b_1-b_2)i$, with $a_1,a_2,b_1,b_2\in\R$.\\
    Set $p=a_1-a_2$ and $q=b_1-b_2$, then we have from $1c$ we know that 
    \begin{align*}
        \sqrt{p^2+q^2}&\leq\sqrt{p^2}+\sqrt{q^2}\\
        \sqrt{(a_1-a_2)^2+(b_1-b_2)^2}&\leq\sqrt{(a_1-a_2)^2}+\sqrt{(b_1-b_2)^2}\\
        |z|&\leq|\Re z|+|\Im z|\\
        |z_1-z_2|&\leq|\Re z_1-\Re z_2|+|\Im z_1-\Im z_2|.
    \end{align*}
    \begin{align*}
        (a_1-a_2)^2&\leq(a_1-a_2)^2+(b_1-b_2)^2\\
        \sqrt{(a_1-a_2)^2}&\leq\sqrt{(a_1-a_2)^2+(b_1-b_2)^2} \\
        |\Re z|&\leq|z|\\
        |\Re z_1-\Re z_2|&\leq|z_1-z_2|.
    \end{align*}
    Combining the two inequalities we arrive at the desired result.
\end{proof}
\stepcounter{section}
\section*{Problem 3}
Prove: If $f$ is continuous and $f(z_0)\neq 0$ then there exists a neighbourhood of $z_0$ on which $f\neq 0$.
\begin{proof}
    Let $f(z_0)$. Set $r=\frac{|f(z_0)-0|}{2}$. We know that all points $f(z)\in D(f(z_0),r)$ are not equal to 0 since they are at most half the distance between $f(z_0)$ and 0. By the continuity of $f$ we we can find $\delta_r>0$ such that $D(z_0,\delta_r)$ is a neighbourhood of $z_0$, and $z\in D(z_0,\delta_r)\Rightarrow f(z)\in D(f(z_0),r)$. Thus, we have that there exists a neighbourhood of $z_0$ such that $f\neq0$. 
\end{proof}
\stepcounter{section}
\section*{Problem 8}
Show that $f(z)=|z|$ is continuous.
\begin{proof}
    Let $s\in\C$ be an arbitrary complex number. We say that a function $f$ is continuous if for all $\varepsilon>0$ there exists $\delta>0$ such that we have $|f(z)-f(c)|<\varepsilon$ whenever $|z-c|<\delta$.\\
    Observe by the reverse triangle inequality we have
    \[
        |f(z)-f(c)|=|z|-|w|=||z|-|w||\leq|z-w|.
    \]
    Now chose $\delta=\varepsilon$. Then whenever $|z-c|<\delta$ we have $|f(z)-f(c)|\leq|z-w|<\delta=\varepsilon$
\end{proof}
\stepcounter{section}
\section*{Problem 9}
What is the largest set on which the function $f(z)=1/(1-e^z)$ is continuous.\\
\textit{Solution.} $f(z)$ is not continuous for values of $z$ at which $1-e^z=0$. Those values of $z$ lie on the unit circle in $\C$, that is points of the form $e^z=1$. This function is continuous everywhere else. The largest set on which it is continuous if $\C\setminus\{z:|e^z|\leq1\}$. It does not suffice to only remove values on the unit cirle in $\C$ because we would have a discontinuity jump when $z$ goes from inside the unit circle to outside the unit circle.
\stepcounter{section}
\section*{Problem 14}
For each of the following sets, state $(i)$ whether or not the set is open and $(ii)$ whether or not the set is closed.
\begin{enumerate}[label=(\alph*)]
    \item $\{z\,|\, \Im z>2\}$
    \begin{enumerate}[label=(\roman*)]
        \item Yes. There the sequence of $z_n=(2+\frac{1}{10^n})i$ exists in the set, but the limit point of the set $2i$ is not a part of the set.
        \item No. This set contains none of its limit points.
    \end{enumerate}
    \item $\{z\,|\, 1<|z|\leq2\}$
    \begin{enumerate}[label=(\roman*)]
        \item No. The point $z=2+0i$ is in this set. Any disk of arbitrary radius centred at $2+0i$, the disk will always contain a point $z,z'$ with $|z|\leq2$ and $|z'|>2$. 
        \item No. There are limit points of this set which are not a part of the set.
    \end{enumerate}
    \item $\{z\,|\, -1< \Re z\leq2\}$
    \begin{enumerate}[label=(\roman*)]
        \item No. The point $z=2+0i$ is in this set. Any disk of arbitrary radius centred at $2+0i$, the disk will always contain a point $z,z'$ with $\Re(z)\leq2$ and $\Re(z')>2$. 
        \item No. There are limit points of this set which are not a part of the set.
    \end{enumerate}
\end{enumerate}
\newpage
\stepcounter{section}
\section*{Problem 16}
For each of the following sets, state $(i)$ whether or not the set is connected and $(ii)$ whether or not the set is compact.
\begin{enumerate}[label=(\alph*)]
    \item $\{z\,|\, -1< \Re z\leq2\}$
    \begin{enumerate}[label=(\roman*)]
        \item Yes. For any two points in this set there is a line entirely in the set between the two. The set is convex.
        \item No. Not closed.
    \end{enumerate}
    \item $\{z\,|\, 2\leq |z|\leq3\}$
    \begin{enumerate}[label=(\roman*)]
        \item Yes. This set is an annulus in $\C$, therefore it is connected.
        \item Yes. Closed and bounded.
    \end{enumerate}
    \item $\{z\,|\, |z|\leq 5, \Im z\geq 1\}$
    \begin{enumerate}[label=(\roman*)]
        \item Yes. This set is teh intersection of two connected sets and is therefore connected.
        \item Yes. Closed and bounded.
    \end{enumerate}
\end{enumerate}
\stepcounter{section}
\section*{Problem 19}
Show the union of any collection of open subsets of $\C$ is open.\\
We want to show that given any collection of open sets $\{G_\alpha\}$ we have that $\bigcup_\alpha G_\alpha$ is also open.
\begin{proof}
    Let $G=\bigcup_\alpha G_\alpha$. If $x\in G$, then $x\in G_\alpha$ for some $\alpha$. Since $G_\alpha$ is open for all $\alpha$ we have that $x$ is an interior point of $G_\alpha$, then we have that $x$ is an interior point of $G$.
\end{proof}
\stepcounter{section}
\section*{Problem 20}
Show that the intersection of any finite collection of open subsets of $\C$ is open.
\begin{proof}
    Let $G_\alpha$ be some finite collection of open sets. Set $H=\bigcap_{\alpha=1}^n G_{\alpha}$. For any $x\in H$ we know that there exists a neighbourhood $N_i$ with radii $r_i$ such that $N_i\subset G_\alpha$ for some $\alpha$. Put
    \[
        r=\min\{r_1,r_2,\dots,r_n\},
    \]
    and $N$ a neighbourhood of $x$ with radius $r$. Then $N\subset G_\alpha$ for $1\leq\alpha\leq n$. Thus, we have that $H$ is open.
\end{proof}
\end{document}